\section{Construct Validity}
In collecting the change vectors, we have disregarded updates and move operations from the changes due to the occurrence of simple refactoring changes with no actual behavioral changes.
However, this may lead to missing some important changes such as changing the method invocation to complete another method invocation or moving an if statement to the next line to change the control flow of the program.
We believe that this sacrificed some of the true positives to eliminate many of the false positives.
For future work, handling precise updates and move conditions will enhance the change collecting accuracy and therefore enhance the ability of {\simfinmo}.

\section{External Validity}
Although we have used six of ASF projects to evaluate our {\simfinmo}, it might not represent all the projects that are in software repositories.
However, the projects are varied in their size, domain, and development time.
So we believe the results of our study have empirical value in the software engineering society.

\section{Internal Validity}
For collecting BIC data we have used the SZZ algorithm \cite{sliwerski2005changes}.
Although the algorithm is often used to collect BIC instances, it has limitations.
The deleted lines from the BFC that are blamed to trace BIC are not always bug inducing as they could be refactoring or cosmetic changes \cite{neto2018impact}.
However, with the circumstances, {\simfinmo} showed the comparable or better performance to the existing baselines.
So we believe that the better algorithm that has better precision in BIC instance collecting will improve the performance of {\simfinmo}.
